scikit-image: Image processing in Python

### 2014-03-31 paper.tex
Make paper compatible with peerJ format

\documentclass[letterpaper,compsoc,twoside]{IEEEtran}
% generated by Docutils <http://docutils.sourceforge.net/>
\usepackage{fixltx2e} % LaTeX patches, \textsubscript
\usepackage{cmap} % fix search and cut-and-paste in Acrobat
\usepackage{ifthen}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage[font={small,it},labelfont=bf]{caption}
\usepackage{float}

@@

%%% Body
\begin{document}
\newcounter{footnotecounter}\title{scikit-image: Image processing in Python}\author{Stéfan van der Walt$^{\setcounter{footnotecounter}{1}1,\setcounter{footnotecounter}{2}2}$%
          \setcounter{footnotecounter}{1}\thanks{1 %
          Corresponding author: \protect\href{mailto:stefan@sun.ac.za}{stefan@sun.ac.za}}\setcounter{footnotecounter}{2}\thanks{2 Stellenbosch University,
Stellenbosch, South Africa}, Johannes L. Schönberger$^{\setcounter{footnotecounter}{3}3}$\setcounter{footnotecounter}{3}\thanks{3 Department of Computer Science,
University of North Carolina at Chapel Hill,
Chapel Hill, NC 27599, USA}, Juan Nunez-Iglesias$^{\setcounter{footnotecounter}{4}4}$\setcounter{footnotecounter}{4}\thanks{4 Victorian Life Sciences Computation Initiative
Carlton, VIC, 3010, Australia}, François Boulogne$^{\setcounter{footnotecounter}{5}5}$\setcounter{footnotecounter}{5}\thanks{5 Department of Mechanical and Aerospace Engineering,
Princeton University, Princeton, New Jersey 08544, USA}, Joshua D. Warner$^{\setcounter{footnotecounter}{6}6}$\setcounter{footnotecounter}{6}\thanks{6 Department of Biomedical Engineering,
Mayo Clinic, Rochester, Minnesota 55905, USA}, Neil Yager$^{\setcounter{footnotecounter}{7}7}$\setcounter{footnotecounter}{7}\thanks{7 AICBT Ltd}, Emmanuelle Gouillart$^{\setcounter{footnotecounter}{8}8}$\setcounter{footnotecounter}{8}\thanks{8 Joint Unit CNRS / Saint-Gobain}, Tony Yu$^{\setcounter{footnotecounter}{9}9}$\setcounter{footnotecounter}{9}\thanks{9 Enthought Inc.}, scikit-image contributors$^{\setcounter{footnotecounter}{10}10}$\setcounter{footnotecounter}{10}\thanks{10 https://github.com/scikit-image/scikit-image/graphs/contributors}\thanks{%

          \noindent%
          Copyright\,\copyright\,2014 Stéfan van der Walt et al. This is an open-access article distributed under the terms of the Creative Commons Attribution License, which permits unrestricted use, distribution, and reproduction in any medium, provided the original author and source are credited.%
        }}\maketitle
          \renewcommand{\leftmark}{PeerJ PrePrints}
          \renewcommand{\rightmark}{SCIKIT-IMAGE: IMAGE PROCESSING IN PYTHON}

\InputIfFileExists{page_numbers.tex}{}{}
\newcommand*{\docutilsroleref}{\ref}
\newcommand*{\docutilsrolelabel}{\label}
\begin{abstract}scikit-image is an image processing library that implements algorithms
and utilities for use in research, education and industry applications.  It
is released under the liberal BSD open source license, provides a well-
documented API in the Python programming language, and is developed by an
active, international team of collaborators.\end{abstract}\begin{IEEEkeywords}image processing, reproducible research, education, visualization\end{IEEEkeywords}

\subsection{Introduction%
  \label{introduction}%
}

@@

\subsection{Getting started%
  \label{getting-started}%
}

@@

\subsection{Library contents%
  \label{library-contents}%
}

@@

\subsection{Data format and pipelining%
  \label{data-format-and-pipelining}%
}

@@

\subsection{Development practices%
  \label{development-practices}%
}

@@

\subsection{Usage examples%
  \label{usage-examples}%
}

\subsubsection{Research%
  \label{research}%
}

@@

\subsubsection{Education%
  \label{education}%
}

@@

\subsubsection{Industry%
  \label{industry}%
}

@@

\subsection{Example: image registration and stitching%
  \label{example-image-registration-and-stitching}%
}

@@

\subsubsection{0. Data loading%
  \label{data-loading}%
}

@@

\subsubsection{1. Feature detection and matching%
  \label{feature-detection-and-matching}%
}
\textquotedbl{}Oriented FAST and rotated BRIEF\textquotedbl{} (ORB) features \cite{ORB} are detected in both
images.  Each feature yields a binary descriptor; those are used to find the
putative matches shown in Figure~\DUrole{ref}{pano} B.\begin{Verbatim}[commandchars=\\\{\},fontsize=\footnotesize]
\PY{k+kn}{from} \PY{n+nn}{skimage.feature} \PY{k+kn}{import} \PY{n}{ORB}\PY{p}{,} \PY{n}{match\PYZus{}descriptors}

@@

\subsubsection{2. Transform estimation%
  \label{transform-estimation}%
}
To filter the matches, we apply RANdom SAmple Consensus (RANSAC) \cite{ransac}, a
common method for outlier rejection. This iterative process estimates
transformation models based on randomly chosen subsets of matches, finally
selecting the model which corresponds best with the majority of matches.  The
new matches are shown in Figure~\DUrole{ref}{pano} C.\begin{Verbatim}[commandchars=\\\{\},fontsize=\footnotesize]
\PY{k+kn}{from} \PY{n+nn}{skimage.transform} \PY{k+kn}{import} \PY{n}{ProjectiveTransform}
\PY{k+kn}{from} \PY{n+nn}{skimage.measure} \PY{k+kn}{import} \PY{n}{ransac}

@@

\subsubsection{3. Warping%
  \label{warping}%
}
Next, we produce the panorama itself. The first step is to find the shape of
the output image by considering the extents of all warped images.\begin{Verbatim}[commandchars=\\\{\},fontsize=\footnotesize]
\PY{n}{r}\PY{p}{,} \PY{n}{c} \PY{o}{=} \PY{n}{image1}\PY{o}{.}\PY{n}{shape}\PY{p}{[}\PY{p}{:}\PY{l+m+mi}{2}\PY{p}{]}

@@

\subsubsection{4. Blending%
  \label{blending}%
}

@@

\subsection{Conclusion%
  \label{conclusion}%
}

@@

\subsection{Acknowledgements%
  \label{acknowledgements}%
}

>>>>

\documentclass[fleqn,12pt]{wlpeerj}
% generated by Docutils <http://docutils.sourceforge.net/>
% modified by Juan Nunez-Iglesias to match wlpeerj format
\usepackage{fixltx2e} % LaTeX patches, \textsubscript
\usepackage{cmap} % fix search and cut-and-paste in Acrobat
\usepackage{ifthen}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{caption}
\usepackage{float}

@@

%%% Body
\title{scikit-image: Image processing in Python}

\author[1,2]{Stéfan van der Walt}
\affil[1]{Corresponding author: \protect\href{mailto:stefan@sun.ac.za}{stefan@sun.ac.za}}
\affil[2]{Stellenbosch University,
          Stellenbosch, South Africa}
\author[3]{Johannes L. Schönberger}
\affil[3]{Department of Computer Science,
          University of North Carolina at Chapel Hill,
          Chapel Hill, NC 27599, USA}
\author[4]{Juan Nunez-Iglesias}
\affil[4]{Victorian Life Sciences Computation Initiative,
          Carlton, VIC, 3010, Australia}
\author[5]{François Boulogne}
\affil[5]{Department of Mechanical and Aerospace Engineering,
          Princeton University,
          Princeton, New Jersey 08544, USA}
\author[6]{Joshua D. Warner}
\affil[6]{Department of Biomedical Engineering,
          Mayo Clinic,
          Rochester, Minnesota 55905, USA}
\author[7]{Neil Yager}
\affil[7]{AICBT Ltd,
          Oxford, UK}
\author[8]{Emmanuelle Gouillart}
\affil[8]{Joint Unit CNRS / Saint-Gobain}
\author[9]{Tony Yu}
\affil[9]{Enthought Inc.,
          Austin, TX, USA}
\author[10]{the scikit-image contributors}
\affil[10]{https://github.com/scikit-image/scikit-image/graphs/contributors}

\keywords{image processing, reproducible research, education, visualization}

\begin{abstract}
scikit-image is an image processing library that implements algorithms
and utilities for use in research, education and industry applications.  It
is released under the liberal BSD open source license, provides a well-
documented API in the Python programming language, and is developed by an
active, international team of collaborators.
\end{abstract}

\begin{document}

\flushbottom
\maketitle
\thispagestyle{empty}

\section*{Introduction}
  \label{introduction}

@@

\section*{Getting started}
  \label{getting-started}

@@

\section*{Library contents}
  \label{library-contents}

@@

\section*{Data format and pipelining}
  \label{data-format-and-pipelining}

@@

\section*{Development practices}
  \label{development-practices}

@@

\section*{Usage examples}
  \label{usage-examples}

\subsection*{Research}
  \label{research}

@@

\subsection*{Education}
  \label{education}

@@

\subsection*{Industry}
  \label{industry}

@@

\section*{Example: image registration and stitching}
  \label{example-image-registration-and-stitching}

@@

\subsection*{0. Data loading}
  \label{data-loading}

@@

\subsection*{1. Feature detection and matching}
  \label{feature-detection-and-matching}

\textquotedbl{}Oriented FAST and rotated BRIEF\textquotedbl{} (ORB) features \cite{ORB} are detected in both
images.  Each feature yields a binary descriptor; those are used to find the
putative matches shown in Figure~\DUrole{ref}{pano} B.\begin{Verbatim}[commandchars=\\\{\},fontsize=\footnotesize]
\PY{k+kn}{from} \PY{n+nn}{skimage.feature} \PY{k+kn}{import} \PY{n}{ORB}\PY{p}{,} \PY{n}{match\PYZus{}descriptors}

@@

\subsection*{2. Transform estimation}
  \label{transform-estimation}

To filter the matches, we apply RANdom SAmple Consensus (RANSAC) \cite{ransac}, a
common method for outlier rejection. This iterative process estimates
transformation models based on randomly chosen subsets of matches, finally
selecting the model which corresponds best with the majority of matches.  The
new matches are shown in Figure~\DUrole{ref}{pano} C.\begin{Verbatim}[commandchars=\\\{\},fontsize=\footnotesize]
\PY{k+kn}{from} \PY{n+nn}{skimage.transform} \PY{k+kn}{import} \PY{n}{ProjectiveTransform}
\PY{k+kn}{from} \PY{n+nn}{skimage.measure} \PY{k+kn}{import} \PY{n}{ransac}

@@

\subsection*{3. Warping}
  \label{warping}

Next, we produce the panorama itself. The first step is to find the shape of
the output image by considering the extents of all warped images.\begin{Verbatim}[commandchars=\\\{\},fontsize=\footnotesize]
\PY{n}{r}\PY{p}{,} \PY{n}{c} \PY{o}{=} \PY{n}{image1}\PY{o}{.}\PY{n}{shape}\PY{p}{[}\PY{p}{:}\PY{l+m+mi}{2}\PY{p}{]}

@@

\subsection*{4. Blending}
  \label{blending}

@@

\section*{Conclusion}
  \label{conclusion}

@@

\section*{Acknowledgements}
  \label{acknowledgements}
